Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2022-12-04 paper/manuscript.Rmd
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., experts should modulate their performance relevant to articulation, but not dynamics).

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings. This may imply that participants prioritised the teaching of articulation and did not modify two performance parameters at the same time. This is consistent with the findings in parental scaffolding where caregivers help infants acquire a complex action sequence by simplifying the action into sub-actions and adding complexity step by step, which enables infants to build up motor repertoires to achieve a goal [@zukow-goldring_2007].

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., expert pianists should modulate their performance relevant to articulation, but not dynamics).

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings. This may imply that participants prioritised articulation over dynamics and did not modify two performance parameters at the same time. This is consistent with the findings in parental scaffolding where caregivers help infants acquire a complex action sequence by simplifying the sequential action into discrete sub-actions and adding complexity step by step [@zukow-goldring_2007]. In our study, expert pianists might have focused on the teaching of articulation first.

### 2022-12-04 paper/manuscript.tex
update discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., experts should modulate their performance relevant to articulation, but not dynamics).

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings. This may imply that participants prioritised the teaching of articulation and did not modify two performance parameters at the same time. This is consistent with the findings in parental scaffolding where caregivers help infants acquire a complex action sequence by simplifying the action into sub-actions and adding complexity step by step, which enables infants to build up motor repertoires to achieve a goal (Zukow-Goldring \& Arbib, 2007).

>>>>

The present study investigated whether and how expert pianists adapt their performance depending on the displayed skills of novices whom they are trying to teach. We created artificial recordings to manipulate the implementation of two musical expressive techniques (i.e., articulation and dynamics) notated on the sheet music. The recordings where the two techniques were implemented were supposed to resemble the performances of students with good skills. The recordings where neither of the two techniques was implemented were supposed to resemble the performances of students with lower skills who had not yet learnt how to implement articulation and dynamics. The recordings where either of the two techniques was implemented but the other was missing were created to examine whether expert pianists could recognise a particular problem that students have (e.g., only articulation was missing) and adjust their performance accordingly (e.g., expert pianists should modulate their performance relevant to articulation, but not dynamics).

Expert pianists exaggerated legato and staccato when articulation was not implemented in the recordings. This is in line with our predictions that experts would exaggerate only the relevant aspects of the performance if a particular technique was missing in the recordings. However, we did not find significant results in terms of dynamics. Instead, we found that expert pianists produced softer piano when articulation was implemented in the recordings, indicating that participants exaggerated piano only when there was no problem with regard to articulation in the recordings. This may imply that participants prioritised articulation over dynamics and did not modify two performance parameters at the same time. This is consistent with the findings in parental scaffolding where caregivers help infants acquire a complex action sequence by simplifying the sequential action into discrete sub-actions and adding complexity step by step (Zukow-Goldring \& Arbib, 2007). In our study, expert pianists might have focused on the teaching of articulation first.
